A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-21 06-appendix.tex
Remove a seção PROBLEMA do apêndice
Adiciona definição da função \pot ao apêndice

  \begin{case}
    $p=\ceu{\Ifelse{\Mem(\Id)}{p'}{p''}}$.  There are two subcases.
    \begin{subcase}
      $\eval(\ceu{\Mem(\Id)})$~is true.
      %%
      Then~$\pi_1$ and~$\pi_2$ are instances of~\R{if-true}.
      Hence~$p_1=p_2=p'$ and~$e_1=e_2=\nil$.
    \end{subcase}
    \begin{subcase}
      $\eval(\ceu{\Mem(\Id)})$ is false.
      %%
      Then~$\pi_1$ and~$\pi_2$ are instances of~\R{if-false}.
      Hence~$p_1=p_2=p''$ and~$e_1=e_2=\nil$.
    \end{subcase}
  \end{case}

@@

  \begin{case}
    $p=\ceu{\Ifelse{\Mem(\Id)}{p'}{p''}}$.
    %%
    There are two subcases.
    \begin{subcase}
      $\eval(\ceu{\Mem(\Id)})$~is true.
      %%
      Then, by~\R{if-true} and by the induction hypothesis, there is
      a~$\delta'$ such that
      \begin{align*}
        \<\ceu{\Ifelse{\Mem(\Id)}{p'}{p''}},n,\nil>
        &\nst[1]\<p',n,e>\\
        &\nst[*]\delta'_\Hnst\,.
      \end{align*}
    \end{subcase}
    \begin{subcase}
      $\eval(\ceu{\Mem(\Id)})$~is false.
      %%
      Then, by~\R{if-false} and by the induction hypothesis, there is
      a~$\delta'$ such that
      \begin{align*}
        \<\ceu{\Ifelse{\Mem(\Id)}{p'}{p''}},n,\nil>
        &\nst[1]\<p'',n,e>\\
        &\nst[*]\delta'_\Hnst\,.
      \end{align*}
    \end{subcase}
  \end{case}

@@

% LocalWords:  subcase subcases

>>>>

  \begin{case}
    $p=\ceu{\IfElse{\Mem(\Id)}{p'}{p''}}$.  There are two subcases.
    \begin{subcase}
      $\eval(\ceu{\Mem(\Id)})$~is true.
      %%
      Then~$\pi_1$ and~$\pi_2$ are instances of~\R{if-true}.
      Hence~$p_1=p_2=p'$ and~$e_1=e_2=\nil$.
    \end{subcase}
    \begin{subcase}
      $\eval(\ceu{\Mem(\Id)})$ is false.
      %%
      Then~$\pi_1$ and~$\pi_2$ are instances of~\R{if-false}.
      Hence~$p_1=p_2=p''$ and~$e_1=e_2=\nil$.
    \end{subcase}
  \end{case}

@@

  \begin{case}
    $p=\ceu{\IfElse{\Mem(\Id)}{p'}{p''}}$.
    %%
    There are two subcases.
    \begin{subcase}
      $\eval(\ceu{\Mem(\Id)})$~is true.
      %%
      Then, by~\R{if-true} and by the induction hypothesis, there is
      a~$\delta'$ such that
      \begin{align*}
        \<\ceu{\IfElse{\Mem(\Id)}{p'}{p''}},n,\nil>
        &\nst[1]\<p',n,e>\\
        &\nst[*]\delta'_\Hnst\,.
      \end{align*}
    \end{subcase}
    \begin{subcase}
      $\eval(\ceu{\Mem(\Id)})$~is false.
      %%
      Then, by~\R{if-false} and by the induction hypothesis, there is
      a~$\delta'$ such that
      \begin{align*}
        \<\ceu{\IfElse{\Mem(\Id)}{p'}{p''}},n,\nil>
        &\nst[1]\<p'',n,e>\\
        &\nst[*]\delta'_\Hnst\,.
      \end{align*}
    \end{subcase}
  \end{case}

@@

\begin{definition}
  The \emph{potency} of a program~$p$, denoted~$\pot(p)$, is defined as
  follows:
  \begin{alignat*}{2}
    \pot(p)&=1
    &\quad &\text{if~$p=\ceu{\EmitInt(e)}$}\\
    %%
    \pot(p)&=\pot(p_1)+\pot(p_2)
    &\quad &
    \begin{aligned}[t]
      &\text{if~$p=p_1;\,p_2$ or~$p=\ceu{p_1\AtLoop{p_2}}$}\\
      &\quad\text{and~$p_1\ne{\ceu{\AwaitExt{e}}}$}
    \end{aligned}\\
    %%
    \pot(p)&=\max\{\pot(p_1),\pot(p_2)\}
    &\quad &
    \begin{aligned}[t]
      &\text{if~$p=\ceu{\IfElse{\Mem(\Id)}{p_1}{p_2}}$}\\
      &\quad\text{or~$p=\ceu{{p_1}\And{p_2}}$
        or~$p=\ceu{{p_1}\Or{p_2}}$}\\
      &\quad\text{or~$p=\ceu{{p_1}\AtAnd{p_2}}$
        or~$p=\ceu{{p_1}\AtOr{p_2}}$}
    \end{aligned}\\
    %%
    \pot(p)&=0
    &\quad &\text{otherwise}\,.
  \end{alignat*}
  % \item$\pot(p)=\pot(p_1)$,\\
  %   \strut\quad if~$p=\ceu{\Loop{p_1}}$ or~$p=\ceu{\Every{e}\,{p_1}}$;
  %   %%
  % \item$\pot(p)=\pot(p_1)+\pot(p_2)$,\\
  %   \strut\quad if~$p=p_1;\,p_2$ or~$p=\ceu{p_1\AtLoop{p_2}}$
  %   and~$p_1\ne{\ceu{\AwaitExt{e}}}$;
  %   %%
  % \item$\pot(p)=\max\{\pot(p_1),\pot(p_2)\}$,\\
  %   \strut\quad if~$p=\ceu{\IfElse{\Mem(\Id)}{p_1}{p_2}}$\\
  %   \strut\qquad or~$p=\ceu{{p_1}\And{p_2}}$ or~$p=\ceu{{p_1}\Or{p_2}}$\\
  %   \strut\qquad or~$p=\ceu{{p_1}\AtAnd{p_2}}$ or~$p=\ceu{{p_1}\AtOr{p_2}}$;
  %   %%
  % \item$\pot(p)=0$,\enspace otherwise.
  % \end{enumerate}
  % \begin{align*}
  %   &\pot(p)=\\
  %   &\enspace\begin{cases}
  %     1
  %     &\text{if~$p=\ceu{\AwaitExt(e)}$}\\[2\jot]
  %     %%
  %     \pot(p_1)
  %     &\text{if~$p=\ceu{\Loop{p1}}$ or~$p=\ceu{\Every{e}{p_1}}$}\\[2\jot]
  %     %%
  %     \pot(p_1)+\pot(p_2)
  %     &\parbox[t]{.6\hsize}{%
  %       if~$p=p_1;\,p_2$ or~$p=\ceu{p_1\AtLoop{p_2}}$\\
  %       \strut\quad and~$p_1\ne{\ceu{\EmitInt{e}}}$}\strut\\[6\jot]
  %     %%
  %     \max\{\pot(p_1),\pot(p_2)\}
  %     &\parbox[t]{.6\hsize}{%
  %       if~$p=\ceu{\IfElse{\Mem(\Id)}{p_1}{p_2}}$\\
  %       \strut\quad or~$p=\ceu{{p_1}\And{p_2}}$\\
  %       \strut\quad or~$p=\ceu{{p_1}\AtAnd{p_2}}$\\
  %       \strut\quad or~$p=\ceu{{p_1}\Or{p_2}}$\\
  %       \strut\quad or~$p=\ceu{{p_1}\AtOr{p_2}}$}
  %   \end{cases}
  % \end{align*}
\end{definition}
